---
title: "Travel"
author: "Biagio Tomasetig"
subtitle: Analyse, Discover, Reignite
output:
  html_document:
    toc: yes
    toc_depth: 5
editor_options:
  markdown:
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE)
```

# Overview

Travelling entails moving from one location to another.
However, the idea of travelling varies from person to person.
For someone, to travel means simply moving from their home to the nearest city; for others, a travel happens only if the distance exceeds a certain number of kilometres.
As subjective as it may be, we all find ourselves travelling when we decide to move for personal or professional reasons.
Even the word used to denote a move from one place to another can change the subjective perception of such move, so using travel, journey, trip can change people intentions.
We will consider the words travel, journey, trip in a broad sense, considering any movement from one place to another, including single-day trips, outside of commonly frequented places.

It is interesting to analyse these movements from one place to another and get to know what kind of information can be extracted and perhaps shared between travel companions or friends.
This raises a lot of questions, ranging from how to collect data, to issues concerning privacy, to people willingness to share such information.
Our goal is to try to understand these kind of relations and analyse such data to study what information are the most useful or helpful for users.

In our research we will study geographic data and the best way to elicit information from those.
Also, we will work with some users' opinions about the use of such data on social networks.
We want to study location-based data and discover the best ideas and approaches to work with this kind of information.
The reason for this research has it's roots in the desire to create a new social network related to travel in a broad sense.
We will not dig deep into the software specifications but we will try to gather as much ideas as possible starting from different types of datasets.
We will present different approaches and apply data science techniques to gain as much knowledge on the topic as possible.

# Data analysis

Our focus is on geographic data and information that we're going to analyse using different techniques and approaches.
We will consider our personal location-based dataset to analyse some ideas on a single user, and we will work with different datasets from on-line sources.
Also, we will work with some data from a specific survey on the relation between travel and social networks.
Going into the details we're going to develop some use cases with different options of the aforementioned types of data.
For example we could consider the relation between geo-spatial points with an evolution overtime, work with some simulations or analyse users behaviours (also with social networks) when travelling.

## Single user GPS data

```{r child = 'single_user_analysis.Rmd'}
```

## Users GPS data

```{r child = 'multi_users_analysis.Rmd'}
```

## Social networks and Travel

```{r child = 'social_analysis.Rmd'}
```

# Recap

The analysis carried out led to interesting results from various points of view.

-   We worked on our personal dataset of geographical trajectories and analysed:

    -   general observations on the composition of geographical trajectories (time between successive points, speed, elevation, map representation from different viewpoints);
    -   an analysis on the most visited municipalities (province and regions);
    -   geohash observations and analysis;
    -   proof of concept related to geohashes and their "value" overtime;
    -   graphs and geohash movements.

-   We briefly considered different datasets from other researches, in particular we explored the geohash composition of such datasets.

-   We analysed the needs and ideas of users when considering a new social network related to travel.

It was interesting to analyse the geographic data points, also in relation to what we remembered as an experience.
We found out that seeing where we were made us remember previous experiences.
This is fascinating and can be extended to a new social network, also based on possible users' ideas.

We answered our questions:

::: {#questions align="center"}
***What can we obtain from a collection of geographical points?***

***What is the relation between travel and social networks?***

***What can make us reignite our desire to explore?***
:::
